### 2014-06-06 related_work.tex
related work

\paragraph{Cascaded detection}\label{cascaded-detection}
Detection cascade \cite{Viola2004,Felzenszwalb-CVPR-2010} is a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order to features/classifiers. This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}. Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade}. While previous cascade schemes really on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.

\paragraph{Dynamic selection}\label{dynamic-selection}
Most recently
  Timely Object Recognition \cite{Karayev-NIPS-2012}
  Cross-talk cascades \cite{Dollar-ECCV-2012}

>>>>

\paragraph{Cascaded detection}\label{cascaded-detection}
Detection cascade \cite{Viola2004,Felzenszwalb-CVPR-2010} is a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order of features/classifiers. This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}. Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade}. While previous cascade schemes rely on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.

\paragraph{Dynamic selection}\label{dynamic-selection}
Most recently, learnt feature and classification deployment schemes based on budget aware policies have shown how to flexibly adapt computation at test time dependent on the input and intermediate results \cite{Karayev-NIPS-2012,karayev14cvpr}. We extend these ideas to the most recent developments of CNNs for visual object detection with a focus on deployment on highly parallel GPU computing hardware. In particular, we effectively combine  dense evaluation of shared, cheap feature with a fine-grained dynamic execution policies reasoning on window proposals for more expensive features.
